Observed vs. Simulated Year Comparison

### 2021-12-11 03-post-process/compare-sim-to-obs.Rmd
Include plots for aggregate quantities in sim vs. obs RMD

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ma_tot[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("Ma_tot[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total LGR Smolt: Estimates")
ratio_plots(x, "Total LGR Smolt: Ratios")
```

@@

>>>>

```{r}
x = append(
  lapply(1:4, function(j) get_ratio("Ma_tot[year,origin,pop]", obs_y, sim_y, pop = j, origin = 1)),
  lapply(1:4, function(j) get_ratio("Ma_tot[year,origin,pop]", obs_y, sim_y, pop = j, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Total LGR Smolt: Estimates")
ratio_plots(x, "Total LGR Smolt: Ratios")
#### Aggregate Total Adult Return (To Tributary)

```{r}
x = append(
  list(get_ratio("Ra_aggregate[year,origin]", obs_y, sim_y, origin = 1)),
  list(get_ratio("Ra_aggregate[year,origin]", obs_y, sim_y, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Aggregate Total Adult Return (To Tributary): Estimates")
ratio_plots(x, "Aggregate Total Adult Return (To Tributary): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Aggregate Total Adult Return (To Tributary)"))
```

#### Aggregate Total Smolt (At LGR)

```{r}
x = append(
  list(get_ratio("Ma_aggregate[year,origin]", obs_y, sim_y, origin = 1)),
  list(get_ratio("Ma_aggregate[year,origin]", obs_y, sim_y, origin = 2))
)
x = do.call(abind, append(x, list(along = 4)))
vals_plots(x, "Aggregate Total Smolt (At LGR): Estimates")
ratio_plots(x, "Aggregate Total Smolt (At LGR): Ratios")
derived_ratios = rbind(derived_ratios, summarize_ratios(x, Class = "Abundance", Type = "Aggregate Total Smolt (At LGR)"))
```

@@

#### Aggregate Total Adult Return (To Tributary) {.tabset .tabset-pills}

```{r, fig.width = 7, fig.height = 4}
ts_plot("Ra_aggregate[year,origin]", origin = 1)
```

```{r, fig.width = 7, fig.height = 4}
ts_plot("Ra_aggregate[year,origin]", origin = 2)
```

#### Aggregate Total Smolt (At LGR) {.tabset .tabset-pills}

```{r, fig.width = 7, fig.height = 4}
ts_plot("Ma_aggregate[year,origin]", origin = 1)
```

```{r, fig.width = 7, fig.height = 4}
ts_plot("Ma_aggregate[year,origin]", origin = 2)
```
